---
title: "datasauRus"
author: "Kasia Banas"
date: "2024-09-26"
output: html_document
---

Install and load the datasauRus library:

```{r}
install.packages("datasauRus")
library(datasauRus)
```

Load the tidyverse: 
```{r}
library(tidyverse)
```

`datasaurus_dozen` is a dataset demonstrating the utility of visualization. 
These 12 datasets are equal in standard measures: mean, standard deviation, 
and Pearson's correlation. But they look very different
Run the chunk below to get more info about this dataset:

```{r}
?datasaurus_dozen
```

See what datasets are in the datasaurus_dozen:

```{r}
datasaurus_dozen %>% # called the pipe - way to link up lines of code 
  distinct(dataset)
```

## Exercise 1
Pick 2 datasets and plot them next to one another
(I'd recommend scatterplot, use facets if you like)

```{r}
library(ggplot2)

dino_data <- datasaurus_dozen %>% 
  filter(dataset=="dino")

dino_data %>% 
  ggplot(aes(x=x, y=y))+
  geom_point(colour = "darkgreen")

bullseye_data <- datasaurus_dozen %>% 
  filter(dataset=="bullseye")

bullseye_data %>% 
  ggplot(aes(x=x, y=y))+
  geom_point(colour = "red") + 

combined_data <- datasaurus_dozen %>% 
  filter(dataset=="dino" | dataset=="bullseye")

combined_data %>% 
  ggplot(aes(x=x, y=y))+
  geom_point(colour = "blue")+
  facet_wrap(~dataset)

```

faster way:
```{r}
datasaurus_dozen %>%
  filter(dataset == "dino" | dataset=="star") %>%  #use OR 
  ggplot(aes(x = x, y = y, colour = dataset)) + 
  geom_point() +
 facet_wrap(~dataset)
  
```


## Exercise 2
For these same two datasets, find the mean and standard deviation
for the x and y variable in each. What did you find? 
```{r}
summary(dino_data) # mean of x = 54.26 , mean of y = 47.832  
summary(bullseye_data) # mean of x = 54.27 , mean of y = 47.831 

sd(dino_data$x) #sd of x = 16.76514
sd(dino_data$y) #sd of y = 26.9354
sd(bullseye_data$x) #sd of x = 16.76924
sd(bullseye_data$y) #sd of y = 26.93573
```

faster way:
```{r}
datasaurus_dozen %>%
  filter(dataset == "dino" | dataset=="star") %>%
  group_by(dataset) %>%
  summarise(mean_x = mean(x), sd_x = (sd(x)), mean_y = mean(y), sd_y = sd(y))

```



